Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-10 latex/comp_or.tex
data50 experiments completed

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                          &                     &\multicolumn{6}{c}{\bf Scenarios}                                                                        &{\bf Normalized}\\
                                                 \cmidrule{4-9}		
{\bf Surplus}         & {$method$}               & {\bf Results}      &{\bf 1}      &{\bf 2}      &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speed-up} \\
\toprule

\multirow{7}{*}{$1.2$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 12.00       & {\bf 8.38}  & {\bf 12.19} & 13.38       &  14.42      & 13.25        &   \\%
&                                                & {\it run-time (s)} &  8          &   14        &  25         &  95         &    217      &  1719        &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 8.37        &  6.40       &  7.68       &  8.05       &   7.72      & 6.74         & \\%
&                                                & {\it run-time (s)} &  < 1        &  < 1        &    3        &   11        &   27        &  342         &\\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 12.24} &  7.95       &  11.59      & {\bf 13.80} & {\bf 16.16} & {\bf 13.74}  &   \\%
&                                                & {\it run-time (s)} &  < 1        &  < 1        &    2        &   6         &    15       &   165        &   \\%

@@

\multirow{7}{*}{$1.5$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 16.49       & 0        & 0 & 13.38       &  0      & 0        &   \\%
&                                                & {\it run-time (s)} &  12         &   14        &  25         &  95         &    217      &  1719        &   \\%

@@

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 16.59} & {\bf 10.49} &  16.82      & 18.46        & 22.19      & {\bf 0}  &   \\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   10         &   27       &   165        &   \\%

@@

For {\it Gurobi} in {\bf Scenario 1}, 50\% of the results were optimal, but the remaining were suboptimal due to the time limit. This explains that {\it mpShims} surpassed {\it Gurobi} results. The same applies to scenarios 4, 5 and 6, where {\it Gurobi} obtained less than 30\% optimal results.

>>>>

We ran Algorithm \ref{alg:main} in the 6 scenarios described in Table \ref{tab:scenarios}, considering 3 methods for node-by-node resolution: {\it Gurobi}, {\it Shims} (Algorithm \ref{alg:shims}), and {\it mpShims} (Algorithm \ref{alg:mpshims}).

In generating the items in each node, we consider 3 values for the parameter ${\it surplus}$. The results obtained for the function $f$, with the corresponding runtime in seconds, are shown in Tables \ref{tab:results} (${\it surplus} = 1.2$, ${\it surplus} = 1.5$, and ${\it surplus} = 2.0$).

For each $method$, $scenario$ and $surplus$, 7 different instances were generated. Therefore, 126 tests (6 scenarios $\times$ 3 volumes $\times$ 7 instances) were performed for each method.

The average tour values were presented for $f$ and, for the runtime, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speed-up}: ratio of the sums of the worst runtimes of all scenarios and the sum of the method runtimes in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

In each $scenario$, we indicate in bold the best value of $f$\/ found. In each table, we also indicate in bold the best {\bf Normalized}\/ and {\bf Speed-up}\/ values.

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                          &                     &\multicolumn{6}{c}{\bf Scenarios}                                                                        &{\bf Normalized}\\
                                                 \cmidrule{4-9}		
{\it surplus}         & {$method$}               & {\bf Results}      &{\bf 1}      &{\bf 2}      &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speed-up} \\
\toprule

\multirow{7}{*}{$1.2$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 12.00       & {\bf 8.38}  & {\bf 12.19} & 13.38       &  14.42      & 13.25        & 0.96 \\% 7651
&                                                & {\it run-time (s)} &  8          &   14        &  25         &  95         &    217      &  1719        & 1.0  \\%2078

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 8.37        &  6.40       &  7.68       &  8.05       &   7.72      & 6.74         & 0.56 \\%
&                                                & {\it run-time (s)} &  < 1        &  < 1        &    3        &   11        &   27        &  342         & 5.4   \\%385

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 12.24} &  7.95       &  11.59      & {\bf 13.80} & {\bf 16.16} & {\bf 13.74}  & {\bf 0.99} \\%
&                                                & {\it run-time (s)} &  < 1        &  < 1        &    2        &   6         &    15       &   165        & {\bf 10.9}  \\% 190

@@

\multirow{7}{*}{$1.5$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 16.49       & {\bf 11.60} & {\bf 16.68} & 18.33       &  20.10      & 17.94        & 0.97  \\%10402
&                                                & {\it run-time (s)} &  12         &   25        &  45         &  169        &   437       &  2377        & 1.0  \\%3065

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 12.53       &  8.31       &  10.04      &  10.94      &   11.72     & 10.13        & 0.61 \\%
&                                                & {\it run-time (s)} &  < 1        &  3          &    6        &   24        &   70        &  419         & 5.9 \\%523

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 16.71} & 10.86       & {\bf 16.68} & {\bf 18.84} & {\bf 21.30} & {\bf 19.39}  & {\bf 1.00}  \\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   9         &   26        &   158        & {\bf 15.4}  \\%199

\midrule
\multirow{7}{*}{$2.0$}&\multirow{2}{*}{ $Gurobi$}& $f$                & 16.49       & {\bf 11.60} & {\bf 16.68} & 18.33       &  20.10      & 17.94        &   \\%
&                                                & {\it run-time (s)} &  12         &   25        &  45         &  169        &   437       &  2377        &   \\%

@@

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & {\bf 16.71} & 10.86       & {\bf 16.68} & {\bf 18.84} & {\bf 21.30} & {\bf 19.39}  &   \\%
&                                                & {\it run-time (s)} &  < 1        &  2          &    3        &   9         &   26        &   158        &   \\%

@@

For {\it Gurobi} in some scenarios, less than 50\% of the results were optimal, and the remaining were suboptimal due to the time limit. This explains that {\it mpShims} surpassed {\it Gurobi} results.
